\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
clarifying initial par

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI to optimize some element of their business
process. Deep Learning~(DL) libraries, such as \jax, \torch{}, and
\tf{}, provide the building blocks for the AI components of these
applications.  Unfortunately, as any piece of software, these
libraries contain bugs. An impressive number of techniques have been
recently proposed to find bugs in these libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge}, 
however we observe that the evaluation of
these techniques do \emph{not} use a reference set of reproducible
bugs to evaluate their effectiveness. The lack of evaluation standards
is an obstacle to the fair comparison of techniques, hindering
research progress.

>>>>

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI as part of their business processes. Deep
Learning~(DL) libraries, such as \jax, \torch{}, and \tf{}, provide
the building blocks for the AI components of these applications.
Unfortunately, as any piece of software, these libraries contain
bugs. An impressive number of techniques have been recently proposed
to find bugs in these
libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
however we observe that the evaluation of these techniques do
\emph{not} use a reference set of reproducible bugs to evaluate their
effectiveness. The lack of evaluation standards is an obstacle to the
fair comparison of techniques, hindering research progress.
